---
title: "README"
author: "Rasmus Kirkegaard"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 10)
```

# MicroBench
Overview of our data for microbial genomic benchmarking

## Data availability

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(readxl)
read_xlsx("data_links.xlsx")
```

Nanopore data

Sample, date of sequencing, sequencing kit,flowcell type,flowcell ID, sample rate, date of basecalling, dorado version, basecall model version, fast, hac, sup, supdup, allmods
ZymoHMW, YYYY-MM-DD, LSK114,FLO-PRO114HD, PAS01578, 5 khz, YYYY-MM-DD, 0.3.4,4.2.0, ftp://ftp.sra.ebi.ac.uk/vol1/run/ERR119/ERR11901474/PAS01578.dna_r10.4.1_e8.2_400bps_sup@v4.2.0.fastq.gz,ftp://ftp.sra.ebi.ac.uk/vol1/run/ERR119/ERR11901474/PAS01578.dna_r10.4.1_e8.2_400bps_sup@v4.2.0.fastq.gz,ftp://ftp.sra.ebi.ac.uk/vol1/run/ERR119/ERR11901474/PAS01578.dna_r10.4.1_e8.2_400bps_sup@v4.2.0.fastq.gz,ftp://ftp.sra.ebi.ac.uk/vol1/run/ERR119/ERR11901474/PAS01578.dna_r10.4.1_e8.2_400bps_supdup@v4.2.0.fastq.gz